An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-05-02 EconGrowth.Rnw
Adjusted the LINEX section text slightly.

The LINEX model has the form

\begin{equation} \label{eq:LINEX_model}
  y = \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} \: e ,
\end{equation}

\noindent where $e$ is one of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.

Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).

>>>>

The LINEX model is given in Equation \ref{eq:LINEX}. Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function in \texttt{R} \citep{R}. Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
